\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2013-04-16 doc/sw-system.tex
Started prob theory write-up

\title[\sw I]
{\SW: Crowd-sourcing the Discovery of Gravitational Lenses. 
I: System Design}

\author[The \SW Collaboration]{%
  The \SW Collaboration:
  % \input{authors.tex}
}

% This list is incomplete.

@@

\date{to be submitted to MNRAS? Not necessarily.}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}

@@

@@

>>>>

\title[\sw I]
{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}

\author[Marshall et al.]{%
  \input{sw-system-authors.tex}
}

@@

\date{to be submitted to MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2013}

@@

\sw is a web-based system that enables the discovery of strong
gravitational lenses in wide-field imaging surveys by arbitrarily large
numbers of people. Carefully produced color composite images are
displayed to the classifiers via a flexible interface, which records
their estimates of the positions of candidate lensed features. Simulated
lenses, and expert-classified non-lenses, are inserted into the stream
at random intervals; this training set is used to give the classifiers
feedback on their performance as well as estimate a dynamically-updated
probability for any given image containing a lens. High probability
systems are filtered into the Zooniverse \Talk discussion system; this
smaller sample is further classified and analysed by volunteers into a
final set. We analyze the classification of the training set itself, and
find that 1) $<$volunteers learn$>$... 2) $<$the filter works$>$...

@@

Our aim is to enable the construction of a sample of good lens
candidates. Since we aspire to making logical  decisions, we define a 
``good candidate'' as one which has a high posterior probability of
being a lens, given the data. The data in our case are the pixel values
of a colour image. However, we can greatly compress these complex,
noisy  datasets by asking our classifiers what they think about them. A
complete  classification in \sw consists of a set of Marker positions,
or none at all. The null set represents the statement from the
classifier that the image in question is $\saidNOT$ a lens, while the
placement of any  Markers indicates that the classifier considers this
image to contain a $\saidLENS$. We simplify the problem ...
